### 2023-05-02 application.tex
up

\mathieu{
resilience never hold in the case of VAS. 
What happens when you add states ? \\
So you consider for instance $q_0(u_k)$ instead of just $u_k$. \\
Everything reachable from $q_0(u_k)$ is still of the form $q(u)$ with u greater than $v_{\Bad}$
(we'd have $v_{\Bad}$ sum of the coordinate of the elements from the basis of $\Bad$ when not considering states).
So now, let us fix some state $q$.
Either there is an element of the basis of $\Bad$ with state $q$.
Then $q(u)$ is necessarily in $\Bad$ (If this hold for all $q \in Q$, then again $k$-resilience does not hold).
Either there is none.
If there is none, then $q(\omega)$ is in the complement of $\Bad$, i.e. $\Safe$.
Then, of course there are probably other elements in $\Safe$ but from
the perspective of $\Bad$ and the extremely high elements $q_i(u_k)$  these ‘smaller’ elements are all but unreachable. 
And the question becomes rather `can we reach $q(\omega)$ from every element of $\Bad$ save from maybe the few smaller ones ?’
Since $q(\omega)$ here is upward-closed this is decidable i.e. it is asking coverability questions. 
It’s not 100\% the question «asking, for every element in the basis of $\Bad$, whether or not $q(0)$ is coverable from it», since you could have, for smaller elements in $\Bad$, other elements of $\Safe$ you can reach, but it seem close.
This would lead to a decision scheme.
Need to write this more formally/properly.}

@@

>>>>

\iffalse
\mathieu{
resilience never hold in the case of VAS. 
What happens when you add states ? \\
So you consider for instance $q_0(u_k)$ instead of just $u_k$. \\
Everything reachable from $q_0(u_k)$ is still of the form $q(u)$ with u greater than $v_{\Bad}$
(we'd have $v_{\Bad}$ sum of the coordinate of the elements from the basis of $\Bad$ when not considering states).
So now, let us fix some state $q$.
Either there is an element of the basis of $\Bad$ with state $q$.
Then $q(u)$ is necessarily in $\Bad$ (If this hold for all $q \in Q$, then again $k$-resilience does not hold).
Either there is none.
If there is none, then $q(\omega)$ is in the complement of $\Bad$, i.e. $\Safe$.
Then, of course there are probably other elements in $\Safe$ but from
the perspective of $\Bad$ and the extremely high elements $q_i(u_k)$  these ‘smaller’ elements are all but unreachable. 
And the question becomes rather `can we reach $q(\omega)$ from every element of $\Bad$ save from maybe the few smaller ones ?’
Since $q(\omega)$ here is upward-closed this is decidable i.e. it is asking coverability questions. 
It’s not 100\% the question «asking, for every element in the basis of $\Bad$, whether or not $q(0)$ is coverable from it», since you could have, for smaller elements in $\Bad$, other elements of $\Safe$ you can reach, but it seem close.
This would lead to a decision scheme.
Need to write this more formally/properly.}
\fi

@@

\mathieu{À priori on devrais avoir la bounded resilience aussi.
En fait, comme on a strong monotony alors
 $\Bad \setminus (\pred^{\leq k}(q_{j_1}(\omega)) \cup \ldots \pred^{\leq k}(q_{j_\ell}(\omega)) )$
 converge vers
  $\Bad \setminus (\pred^{*}(q_{j_1}(\omega)) \cup \ldots \pred^{*}(q_{j_\ell}(\omega)) )$.
  Une fois que le set est stable alors, encore une fois, si il est infini on n'a pas la $k$-résilience
(pour tout $k$ à partir de ce rang là, du coup)
et si il est fini alors on peut vérifier, pour chaque élément, si il est possible d'atteindre
$\Safe$. Si il est possible pour chaque élément alors on prends le maximum des chemins depuis chacun de ces éléments et on fait le max de ça et le $k$ qui permet d'atteindre $\pred^{\leq k} = \pred^*$ pour les $q(\omega)$ ci-dessus et ça nous donne un $k_{\max}$ pour lequel on a la $k_{\max}$-résilience.
Si il est pas possible pour chaque élément alors ça veut dire il y a un élément qui atteindra jamais $\Safe$ et on n'a pas la bounded resilience ni la résilience d'ailleurs. 
Il faut vérifier que c'est possible pour une configuration de vérifier qu'elle est capable d'atteindre $\Safe$ downward closed. 
Normalement c'est le cas d'après Okzan (ils disent c'est équiv du submarking pb).}
